---
title: "Simple Linear Regression"
author: "Said Sharify"
date: "2022-08-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

&nbsp;<br>

## Simple Linear Regression
The first thing we do, is to check if the data is linear or not:
```{r plot data}
library("readr")
WCAT <- read_csv("WCAT.csv")
plot(WCAT$Waist, WCAT$AT)
```

We have :

 - The correlation is positive,
 - The strength of the correlation sounds moderate,
 - We can also see a linear relationship.
 

&nbsp;<br>

#### Checking the strength of the correlation
```{r Correlation}

cor(WCAT$Waist, WCAT$AT)

```
For the value $r = 0.8185578$, we can say it is moderate (and not stronge) as it is smaller than $0.85$.

&nbsp;<br>

####  Linear Regression model
We can use the lm() function to extract X ~ Y values.
```{r Linear Regression model}

rgistr <- lm(WCAT$Waist ~ WCAT$AT)
summary(rgistr)

```
&nbsp;<br>

Knowing :
$$ Y = β0 + β1 .(Input) $$
This equation is used to predict the future values.
In this example we need to predict the AT value. 

So we have :

 - Intercept value = $β0$ = 72.16332
 - WCAT$AT  value = $β1$ = 0.19372

And the equation is :
$$ AT = (72.16332 + 0.19372).(WC) $$
&nbsp;<br>

As the probability associated with a single value is always 0, we need to calculate the range. First, we look at the value of $Pr$. This value will help us to know if the Intercept value and AT value are sufficient to predict the future.  

Here the $Pr$, or probability value is calculated as below:
$Pr =  <2e-16$

With :
$Pr < 0.05$
This two values are statistically significant to be used in our prediction.


&nbsp;<br>

We also have to check the $R-squared:   0.67$ value,
usually it should be greater than 0.8 for a good prediction model. 

&nbsp;<br>

Insted of getting a single value (Y or AT), we can use R to calculate the confidence interval. 
```{r confidence interval}

confint(rgistr,  level = 0.95)

```
So we have the interval :

 - AT(lower range) = 69.1212260 + 0.1676639 .(Input)
 - AT(upper range) = 75.2054046 + 0.2197684 .(Input)

&nbsp;<br>

In order to predict the future with R, we can use the predict function which will predict the values based on the input data :

```{r predict}

predict(rgistr,  interval = "predict")

```
&nbsp;<br>

###  Transformation
#### Logarithmic
In order to increase the accuracy of the model, and apply the logarithmic model on the trend line, we can use this function in R : 
```{r Logarithmic Transformation}

rgistr_log <- lm(WCAT$AT ~ log(WCAT$Waist))
summary(rgistr_log)
confint(rgistr_log, level = 0.95)

```
We can see the values are changed slightly, as the equation is changed as below :

 - AT = -1328.34 + 317.14 ($log$(Input))

&nbsp;<br>

#### Exponential
We can also apply the exponential option over the trend line. 
```{r Exponential Transformation}

rgistr_exp <- lm(log(WCAT$AT) ~ (WCAT$Waist))
summary(rgistr_exp)
confint(rgistr_exp, level = 0.95)
```
So the equation is changed as below :

 - $log$(AT) = 0.741021 + 0.040252 (Input)
 - AT = $exp$ (0.741021 + 0.040252 (Input))


&nbsp;<br>

#### Polynomial 
We also have the Polynomial model to apply on the trend line, which transform the response variable into a polynomial series of the specified degree : 

```{r Polynomial Transformation}

rgistr_pol <- lm((WCAT$AT) ~ (WCAT$Waist) + (WCAT$Waist)^2 + (WCAT$Waist)^3)
summary(rgistr_pol)
confint(rgistr_pol, level = 0.95)
```


&nbsp;<br>

#### Note
Calculated values from these transformations, could be used in Tableau to visualize different presentations of data over the trend line.


&nbsp;<br>

&nbsp;<br>

